---
name: Rhiana
surname: Le
position: "Strategic Marketing"
phone: "+1 (714) 467-9019"
email: "vythuy204@gmail.com"
github: "hirhiana"
linkedin: "lethanhthuyvy"
date: "`r format(Sys.Date(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
  pdf_document: default
header-includes:
  - \usepackage{enumitem}
  - \setlist[itemize]{nosep, left=0pt}
  - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

MBA candidate with a background in Biochemistry and hands-on experience in digital marketing, social media strategy, and international business development. Skilled in data-driven campaigns, brand storytelling, and expanding global market reach. Enthusiastic about innovation, attractiveness, and leveraging marketing analytics to promote quantifiable growth and interaction

# Technical Skills

-   **Programming Languages:** R, Python.
-   **Web Technologies:** HTML, CSS/SCSS, Quarto.
-   **Marketing Tools:** Meta Business Suite, Google Analytics, Canva.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
"Master of Business Administration MBA", "2025 – Expected 2027", "Business Administration", "California State Polytechnic University, Pomona",
  "Bachelor of Science", "2018 – 2022", "Biochemistry", "University of Science – VNU HCM"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "Aug 2022 – Jan 2025", "DM&C Co. Ltd – Black Rouge Vietnam",
  list(
    "Planned and executed integrated branding campaigns across digital and social platforms, increasing reach by 121% and engagement by 98%.",
    "Developed content for the brand website, contributing to a 76% increase in revenue.",
    "Researched customer insights and buying behavior to design in-store activations and boost brand awareness.",
    "Built long-term partnerships with media, influencers, and KOLs/KOCs.",
    "Collaborated with the E-commerce team to uplift sales by 30%.",
    "Worked cross-functionally with marketing, design, and content teams.",
    "Supported CEO with various strategic marketing tasks."
  ),
  "Content Creator",

  "Apr 2023 – Present", "Freelance",
  list(
    "Launched and managed social media campaigns with an 18% increase in followers and 47% higher engagement.",
    "Grew a TikTok account to 11,000+ followers; several videos gained 1M+ views."
  ),
  "Social Media Manager"
) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```
